Irt plot extra

### 2022-02-22 manuscript.Rmd
flowchart highlighted

                    graph [fontname = Helvetica,layout = dot,fontsize = 45,layout = dot ]

                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 2, 
                    fixedsize = true,fontsize = 45]

                    A[label = 'Initial development of 48 items'] 
                    B[label = 'Large scale survey (n=690)']
                    C[label = 'Initial item analysis']
                    D[label = 'Exploratory factor analysis (48 items; n=428)']

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
                    fixedsize = true, fontsize = 45]
                    E[label = 
                    <Factor identification<br/>Scree plot: 6 factors<br/>Minimum average partial method: 5 factors<br/>Hull method: 5 factors>
                    ]

                     subgraph cluster_1 {
                      graph[fontname = Helvetica, shape = box, style =dashed]

                     node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
                    fixedsize = true, fontsize = 45,style =dashed]

                     1[label = '5 factor solution retained 25 items']
                     2[label = <Reliability analysis on EFA sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]

                     3[label = <Confirmatory factor analysis<br/>on the five factor model (25 items; n=262)<br/>Acceptable fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]

                    4[label = <Confirmatory factor analysis<br/>on the five factor model (23 Items; n=262)<br/>Acceptable fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
                     5[label = <Reliability analysis (23 items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
                    8[label = <Measurement invariance analysis (n=262)<br/>Residual measurement invariance achieved>]
                    9[label = <Semantic analysis (n=262):<br/>Semantic scale network analysis<br/>Readbility: grade level 3.33>]
                    10[label = <LEBA short form (18 Items; n=690)<br/>Based on Item Response Theory>]
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
                fixedsize = true, fontsize = 45 ]
                    6[label = 
                    <6 factor solution:<br/>One factor emerged with only two salient loadings>
                    ]
                    7[label = 'Rejected']
                    }

                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->D
                     D ->E
                E ->1
                     1 ->2
                     2 ->3
                     3 ->4
                     4 ->5
                    5->8
                    8 ->9
                    9 ->10
                     E ->6
                     6 ->7

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 800 )
```

>>>>

                    graph [fontname = Helvetica,layout = dot,fontsize = 45 ]

                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 20, height = 3, 
                    fixedsize = true,fontsize = 45]

                    A[label = 'Initial development of 48 items'] 
                    B[label = 'Large scale survey: first round (n=428)']
                    C[label = 'Initial item analysis']
                    D[label = 'Exploratory factor analysis (48 items; n=428)']

                    E[label = 
                    <Factor Identification Method<br/>Scree plot<br/>Minimum average partial method<br/>Hull method>
                    ]

                    F[label = 'Reliability analysis on latent stucture obtained in EFA (n=428)']
                    G[label = 'Large scale survey: second round (n=262)']

                    H[label = 'Confirmatory factor analysis ( n=262)']

                    I[label = 'Reliability analysis on latent stucture obtained in CFA (n=262)']

                    K[label = 'Long LEBA: 23-item', style = filled, fillcolor = Beige]

                    L[label = 'Measurement invariance analysis (n=262)']
                    M[label = 'Semantic analysis (n=262)']
                    N[label = 'Item Response Theory based analysis on the combined sample (n=690)']

                    O[label = 'Short LEBA: 18-item',style = filled, fillcolor = Beige]

                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->D
                     D ->E
                     E ->F
                    F ->G
                     G ->H
                     H ->I
                     I ->K

                    K->L
                    L ->M
                    M ->N
                    N->O

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long form (23-item) and short form (18-item) of LEBA. ', out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 600 )
```
